An efficient acyclic contact planner for multiped robots

### 2016-12-12 body/overview.tex

The second stage extends the guide path into a sequence of contact configurations (Figure~\ref{fig:framework}--\Pb).
With a fixed root position, the dimensionality of the 
contact generation problem is reduced to the number of degrees of freedom of the considered limb. 
%In other words, we consider each limb as a manipulator attached to the root. 
We select from a database of precomputed limb configurations (independent from the environment) the ones resulting in the end-effector being close to the environment.
Limiting our selection to this set of precomputed configurations allow us to drastically reduce the computation times. 
Then we select one of these configurations based on user-defined heuristics (Figure~\ref{fig:contact_gen}), which we present in Section~\ref{sec:heuristics}.

>>>>

The second stage extends the guide path into a sequence of contact configurations (Figure~\ref{fig:framework}--\Pb).
With a fixed root position, the dimensionality of the 
contact generation problem is reduced to the number of degrees of freedom of the considered limb. 
%In other words, we consider each limb as a manipulator attached to the root. 
We select from a database of precomputed limb configurations (independent from the environment) the ones resulting in the end-effector being close to the environment.
Limiting our selection to this set of precomputed configurations allow us to drastically reduce the computation times. 
Then we select one of these configurations based on user-defined heuristics (Figure~\ref{fig:contact_gen}), which we present in the Appendix~\ref{sec:heuristics}.

### 2016-12-12 body/results.tex

\subsubsection{Success rates:}
Table~\ref{tab:requestpercent} summarizes the success rates obtained for each scenario.
We observe that, as expected, our planner does not succeed systematically, because of the approximations made in our formulation. The extreme situation of the car egress scenario provides the less satisfying results in terms of kinematic failure. This is not
surprising considering the narrowness of the scene.
From a pragmatic point of view, regarding the computation times, we claim that our approach provides a satisfying compromise between completeness and efficiency.
Indeed, the advantage of the framework is that when the contact generation fails, it does so rapidly, which allows us to rapidly re-plan a new contact sequence with a reasonable chance of success.
The most efficient (and immediate) approach is probably to launch in parallel several instances of the planner for a given problem (our current implementation is single threaded) and to apply any successful result.

>>>>

\subsubsection{Success rates:}
Table~\ref{tab:requestpercent} summarizes the success rates obtained for each scenario.
As expected, our planner does not succeed systematically, because of the approximations made in our formulation. The extreme situation of the car egress scenario provides the less satisfying results in terms of kinematic failure. This is not
surprising considering the narrowness of the scene.
\deladp{From a pragmatic point of view, }regarding \deladp{the} computation times, \deladp{we claim that} our approach provides a satisfying compromise between completeness and efficiency.
Indeed, \deladp{the advantage of the framework is that} when the contact generation fails, it does so rapidly, which allows us to rapidly re-plan \deladp{a new contact sequence} with a reasonable chance of success.
The most efficient (and immediate) approach is probably to launch in parallel several instances of the planner \deladp{for a given problem} (our current implementation is single threaded) and to apply any successful result.
